Adaptative neigbouring methods applied to telephonic base stations

### 2024-08-14 article.tex
Graphs et critères expliqués

\documentclass[lettersize,journal]{IEEEtran}
\usepackage[utf8]{inputenc}
\usepackage{amsmath,amsfonts}
\usepackage{algorithmic}
\usepackage{algorithm}
\usepackage{array}
\usepackage[caption=false,font=normalsize,labelfont=sf,textfont=sf]{subfig}
\usepackage{textcomp}
\usepackage{stfloats}
\usepackage{url}
\usepackage{verbatim}
\usepackage{graphicx}
\usepackage{cite}
\usepackage{booktabs}
\usepackage[acronym]{glossaries}
\usepackage[unicode=true,pdfusetitle,
 bookmarks=true,bookmarksnumbered=false,bookmarksopen=false,
 breaklinks=false,pdfborder={0 0 0},pdfborderstyle={},backref=false,colorlinks=true]
 {hyperref}
\hypersetup{
 urlcolor=blue, linkcolor=black}
\hyphenation{op-tical net-works semi-conduc-tor IEEE-Xplore}

@@

\newacronym{arcep}{ARCEP}{French Regulatory Authority for Electronic Communications and Posts}
\newacronym{anfr}{ANFR}{French National Frequency Agency}

\begin{document}
\maketitle

@@

\begin{table}[!b]
    \centering
    \caption{Description of the dataset}
    \label{data_columns}
    \begin{tabular}{ll}
        \toprule
        \textbf{Column} & \textbf{Description} \\
        \cmidrule(lr){1-2}
        \textsl{BS\_anfr\_id} & \acrshort{anfr} base station ID \\ 
        \textsl{x, y, latitude, longitude} & Base station coordinates \\ 
        \textsl{nom\_reg, nom\_dep, nom\_com} & Additional location information \\  
        \textsl{site\_2g, 3g, 4g, 5g} & Technology used by the base station \\ 
        \bottomrule
    \end{tabular}
\end{table}

@@

\section{Finding potential neighbours}
\noindent When we are looking for neighbours, we need, at first, a list of potential neighbours for each base stations.
Here are the different methods we can use to solve this problem:

@@

The principle is really close to the one presented before. Let $G$

\subsection{$k$-NN graph}

>>>>

\documentclass[lettersize,journal,english]{IEEEtran}
\usepackage[T1]{fontenc}
\usepackage[utf8]{inputenc}
\usepackage{amsmath,amsfonts}
\usepackage{algorithmic}
\usepackage{algorithm}
\usepackage{array}
\usepackage[caption=false,font=normalsize,labelfont=sf,textfont=sf]{subfig}
\usepackage{textcomp}
\usepackage{stfloats}
\usepackage{url}
\usepackage{verbatim}
\usepackage{graphicx}
\usepackage{cite}
\usepackage{booktabs}
\usepackage{units}
\usepackage[acronym]{glossaries}
\usepackage[unicode=true,pdfusetitle,
 bookmarks=true,bookmarksnumbered=false,bookmarksopen=false,
 breaklinks=false,pdfborder={0 0 0},pdfborderstyle={},backref=false,colorlinks=true]
 {hyperref}
\hypersetup{
 urlcolor=blue, linkcolor=black}
\hyphenation{op-tical net-works semi-conduc-tor IEEE-Xplore}

@@

\newacronym{arcep}{ARCEP}{French Regulatory Authority for Electronic Communications and Posts}
\newacronym{anfr}{ANFR}{French National Frequency Agency}
\newacronym{bs}{BS}{Base Station}

\usepackage[english,french]{babel}

\begin{document}
\selectlanguage{english}
\maketitle

@@

\begin{table}[!b]
    \centering
    \caption{Description of the dataset}
    \label{data_columns}
    \begin{tabular}{ll}
        \toprule
        \textbf{Column} & \textbf{Description} \\
        \cmidrule(lr){1-2}
        \textsl{BS\_anfr\_id} & \acrshort{anfr} \acrshort{bs} ID \\ 
        \textsl{x, y, latitude, longitude} & Base station coordinates \\ 
        \textsl{nom\_reg, nom\_dep, nom\_com} & Additional location information \\  
        \textsl{site\_2g, 3g, 4g, 5g} & Technology used by the \acrshort{bs} \\ 
        \bottomrule
    \end{tabular}
\end{table}

@@

\section{Finding potential neighbours}
\noindent When we are looking for neighbours, we need, at first, a list of potential neighbours for each \acrfull{bs}.
Here are the different methods we can use to solve this problem:

@@

Formally, it is the graph $G$ with vertex set $S$ in which any two distinct points $p\in S$ and $q\in S$ are adjacent precisely when the closed disc having pq as a diameter contains no other points.

\subsection{$k$-NN graph}
\noindent Nevertheless, the two methods presented above are triangulation, that is to say that they do not connect each \acrshort{bs} to all of its potential neighbours.

One simple idea to get rid of this problem could be solved by connecting each \acrshort{bs} to its $k$ nearest neighbours.

\section{Finding the real neighbours}

\noindent Each of the precedent methods gives us a list of potential neighbours for each \acrshort{bs}. However, we know that some of this neighbouring connexions are wrong,
because some \acrshort{bs} will be \og hidden\fg{} by others.

Thus, we need to find methods to suppress bad connexions. That was made by Delphine.

The main innovation of our work is to take in account the difference of \acrshort{bs}'s density.

\subsection{Measurement of \acrshort{bs} density}
\noindent To simplify the explanation, and because it is related, we will assume that solving this problem is equivalent to finding the \acrshort{bs} situated in \og cities\fg{}.

\subsubsection{DBScan}

\subsubsection{HDBScan}

\subsubsection{$3$-NN mean distance}
One provider $\gamma$

To classify each base station we need a method. Here, we will take the mean distance to the 3 nearest neighbours.

Let's call this value $\gamma$, in $\unit{km}$. So, we have 4 different categories.
For each category, we will apply a different distance and angle criterion :

\subsection{Filtering criteria}

\begin{table}[!b]
    \centering
    \caption{Summary of criteria values}
    \label{crit_summary}
    \begin{tabular}{clcc}
        \toprule
        \textbf{$\gamma$} & \textbf{Description} & \textbf{max\_distance} & \textbf{min\_angle} \\
        \cmidrule(lr){1-4}
        $\left[0, 1\right]$ & city center & $\unit[2]{km}$ & $5^\circ$ \\
        $\left]1, 2\right]$ & urban area & $\unit[5]{km}$ & $10^\circ$ \\
        $\left]2, 4\right]$ & extra-urban area & $\unit[10]{km}$ & $15^\circ$ \\
        $\left]4, \infty\right[$ & courntryside & $\unit[15]{km}$ & $20^\circ$ \\
        \bottomrule
    \end{tabular}
\end{table}

\begin{figure}[!t]
    \centering
    \includegraphics[width=2.5in]{images/illus_crit/points.png}
    \caption{Example of a Delaunay triangulation}
    \label{crit_pts}
\end{figure}

\begin{figure}[!b]
    \centering
    \includegraphics[width=2.5in]{images/illus_crit/distance_elim.png}
    \caption{Example of a Delaunay triangulation}
    \label{crit_dis}
\end{figure}

\begin{figure}[!t]
    \centering
    \includegraphics[width=2.5in]{images/illus_crit/angle_elim.png}
    \caption{Example of a Delaunay triangulation}
    \label{crit_ang}
\end{figure}

\begin{figure}[!b]
    \centering
    \includegraphics[width=2.5in]{images/illus_crit/quadrant_elim.png}
    \caption{Example of a Delaunay triangulation}
    \label{crit_qua}
\end{figure}

\begin{figure}[!t]
    \centering
    \includegraphics[width=2.5in]{images/illus_crit/neighs.png}
    \caption{Example of a Delaunay triangulation}
    \label{crit_nei}
\end{figure}

\subsubsection{Distance criterion}
Each \acrshort{bs} has its proper coverage area, which is not infinite. As a matter of fact, we need to suppress longer edges.

\subsubsection{Angle criterion}
For each \acrshort{bs}, we

\subsubsection{Quadrant criterion}
